---
title: Multi-sensor Earth Observation in Practice
subtitle: Summer School

# Summary for listings and search engines
summary: This content will be populated very soon.

# Link this post with a project
projects: []

# Date published
date: "2022-08-09T00:00:00Z"

# Date updated
lastmod: "2022-08-09T00:00:00Z"

# Is this an unpublished draft?
draft: false

# Show this page in the Featured widget?
featured: true

# Featured image
# Place an image named `featured.jpg/png` in this page's folder and customize its options here.
image:
  caption: 'Flight planning using DroneLink'
  focal_point: ""
  placement: 2
  preview_only: false

authors:
- admin

tags:
- CDE 
- summer school 
- drones 
- remote sensing

categories:
- CDE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
